
### Reproduceability

Seed was set as 2014 for this work, which is thus reproduceable.

### Analysis, codes and results

##### Install & load packages, seed
```{r}
library(caret)
library(randomForest) 
library(rpart) 
library(rpart.plot) 
set.seed(2014)
```

##### Data processing

```{r}
training <- read.csv("C:/Users/Kaifeng/Desktop/Practical_Machine_Learning_Project1/pml-training.csv", na.strings=c("NA","#DIV/0!", ""))
testing <- read.csv("C:/Users/Kaifeng/Desktop/Practical_Machine_Learning_Project1/pml-testing.csv", na.strings=c("NA","#DIV/0!", ""))

training<-training[,colSums(is.na(training)) == 0]
testing <-testing[,colSums(is.na(testing)) == 0]
training <-training[,-c(1:7)];testing <-testing[,-c(1:7)]
```

##### Data partition for cross validation

```{r}
subsamples <- createDataPartition(y=training$classe, p=0.7, list=FALSE)
CVtraining <- training[subsamples, ] 
CVtesting <- training[-subsamples, ]
# summary of the CV datasets
summary(CVtraining$classe);summary(CVtesting$classe)
```

##### Method 1: Decision Tree (DT)

```{r}
model1 <- rpart(classe ~ ., data=CVtraining, method="class")
prediction1 <- predict(model1, CVtesting, type = "class")
# accurary assessment
confusionMatrix(prediction1, CVtesting$classe)
```


##### Method 2: Random Forest (RF)

```{r}
model2 <- randomForest(classe ~. , data=CVtraining, method="class")
prediction2 <- predict(model2, CVtesting, type = "class")
# accurary assessment
confusionMatrix(prediction2, CVtesting$classe)
```

##### Comparision & conclusion

As we can see, accurary rate of RF=0.9956>0.7415=accurary rate of DT. Thus RF is chosen for predictive popurse, with expected out of sample error, 1-0.9956=0.0044.

##### Prediction

```{r}
predictfinal <- predict(model2, testing, type="class")
```

##### Function to generate files with predictions to submit for assignment

```{r}
pml_write_files = function(x){  n = length(x)  
for(i in 1:n){    filename = paste0("problem_id_",i,".txt")    
write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)  }}
pml_write_files(predictfinal)
```
